A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-03-17 paper/paper1/ms.tex
Small amount of text added.

\begin{figure}
    \includegraphics[width=\linewidth]{figures/tf2018_fig2_update2023_HAT.png}
    \caption{Mass-radius trends for inflated hot sub-Saturns and hot Jupiters, form modeled after Figure 2 from \citet{2018AJ....155..214T} and updated with NASA Exoplanet Archive confirmed planets.  The trend lines show mass-radius relationship for equilibrium temperatures of 500, 1000, 1250, 1500, and 2000 K, assuming the mean composition and mean heating efficiency from the original figure.  HAT-P-67~b stands alones as occupying the ``Ohmic Dissipation Ridge'', defined by the lack of inflated sub-Saturns.}
    \label{fig:murrayClaySchematic}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{figures/tf2018_fig2_update2023_HAT.png}
    \caption{Mass-radius trends for inflated hot sub-Saturns and hot Jupiters, form modeled after Figure 2 from \citet{2018AJ....155..214T} and updated with NASA Exoplanet Archive confirmed planets.  The trend lines show mass-radius relationship for equilibrium temperatures of 500, 1000, 1250, 1500, and 2000 K, assuming the mean composition and mean heating efficiency from the original figure.  HAT-P-67~b stands alones as occupying the ``Ohmic Dissipation Ridge'', defined by the lack of inflated sub-Saturns, and explained by short lifetimes form runaway inflation and mass loss.}
    \label{fig:murrayClaySchematic}
\end{figure}
